Paper Analysis

### 2025-04-30 Paper_WriteUp/Paper_Plots.qmd
adding standardization to RDs chunk

start = Sys.time()
init_data <- tidy_games |>
  mutate(WhiteElo = as.numeric(WhiteElo),
         BlackElo = as.numeric(BlackElo),
         focal_user = ifelse(focal_white == 1, White, Black),
         elo_diff = ifelse(focal_white == 1,
                           WhiteElo - BlackElo, BlackElo - WhiteElo),
         focal_id = match(focal_user, users),
         focal_rating = ifelse(focal_white == 1, WhiteElo, BlackElo),
         opp = ifelse(focal_white == 1, Black, White),
         opp_rating = ifelse(focal_white == 1, BlackElo, WhiteElo),
         UTCDateTime = ymd_hms(paste0(UTCDate, "_", UTCTime))) |>
  dplyr::select(focal_user, focal_id, focal_white, WhiteElo, BlackElo, White, Black,
                focal_win_prop, elo_diff, focal_result, opp, opp_rating,
                focal_rating, UTCDateTime) |>
  group_by(focal_id) |>
  mutate(time_diff = UTCDateTime - lag(UTCDateTime, default = NA), #default is to ensure first game is always start of a new session
         cum_win_prob = cummean(focal_result), #the mean win probability for the focal player up to the ith (current) game 
         ave_prop = ifelse(time_diff > 300 | is.na(time_diff),  
                           cum_win_prob, #if games played in different session, history is their mean win prob up to the current game
                           lag(focal_win_prop))) |> #if game played in same session, rolling mean over the past n games, removing standardization 
  filter(focal_result != 0.5) %>%
  ungroup()

>>>>

start = Sys.time()
init_data <- tidy_games |>
  mutate(WhiteElo = as.numeric(WhiteElo),
         BlackElo = as.numeric(BlackElo),
         focal_user = ifelse(focal_white == 1, White, Black),
         elo_diff = ifelse(focal_white == 1,
                           WhiteElo - BlackElo, BlackElo - WhiteElo),
         focal_id = match(focal_user, users),
         focal_rating = ifelse(focal_white == 1, WhiteElo, BlackElo),
         opp = ifelse(focal_white == 1, Black, White),
         opp_rating = ifelse(focal_white == 1, BlackElo, WhiteElo),
         UTCDateTime = ymd_hms(paste0(UTCDate, "_", UTCTime))) |>
  dplyr::select(focal_user, focal_id, focal_white, WhiteElo, BlackElo, White, Black,
                focal_win_prop, elo_diff, focal_result, opp, opp_rating,
                focal_rating, UTCDateTime) |>
  group_by(focal_id) |>
  mutate(time_diff = UTCDateTime - lag(UTCDateTime, default = NA), #default is to ensure first game is always start of a new session
         cum_win_prob = cummean(focal_result), #the mean win probability for the focal player up to the ith (current) game 
         ave_prop = ifelse(time_diff > 300 | is.na(time_diff),  
                           0, #if games played in different session, history is their mean win prob up to the current game
                           lag(focal_win_prop) - cum_win_prob)) |> #if game played in same session, rolling mean over the past n games, removing standardization 
  filter(focal_result != 0.5) %>%
  ungroup()
